### 2021-06-30 src/paper/appendix_data.tex
Move synthetic population todos to comment.

\subsection{The Synthetic Population \comment[id=K]{To be written}}

@@

We sample households to build our synthetic population of over one million households
keeping for each individual their age, gender, occupation and whether they work on
Saturdays and Sundays. For each household we draw its county and set the corresponding
federal state.% county is not part of the microcensus campus file
We draw for young children whether they attend a nursery or not \citep{Destatis2020}.

\begin{itemize}
    \item \textcolor{red}{describe how we create the contact model group ids for school,
    work and other}
    \item \textcolor{red}{Describe work contact priority, educ contact priority and
    rapid test compliance parameter and quarantine compliance.}
    \item \textcolor{red}{vaccination rank creation}
\end{itemize}

>>>>

\subsection{The Synthetic Population}

@@

We sample households to build our synthetic population of over one million households
keeping for each individual their age, gender, occupation and whether they work on
Saturdays and Sundays. For each household we draw its county and set the corresponding
federal state.% county is not part of the microcensus campus file
We draw for young children whether they attend a nursery or not
\citep{Destatis2020}.\comment[id=K]{Missing still:
    \begin{itemize}
        \item describe how we create the contact model group ids for school,
        work and other
        \item describe work contact priority, educ contact priority and
        rapid test compliance parameter and quarantine compliance.
        \item vaccination rank creation
    \end{itemize}
}
